### 2020-05-24 abstract.tex
template and double-blind

\begin{abstract}
\label{abstract}
We use smartphones everywhere and concerns have arisen about ‘shoulder surfing’, or the act of strangers peeking at our phone in public areas. This privacy threat have been studied heavily and various countermeasures have been designed, but mainly against attackers with the naked eye. With the development of smartphones and super resolution (SR) technology, however, we believe that this threat have been underestimated, as a malicious observer can attack from farther away with the assist of his smartphone camera and SR algorithms. We underline this concern by presenting SRPeek, an end-to-end system of shoulder surfing, containing a unique multi-image SR neural network architecture designed for this task, which in this application outperforms other known SR algorithms and fills the blank space of multi-image SR. We prove that our attack is efficient, allowing a human to read 95\% of the text off a smartphone screen at 1.5m range (in the experiment’s circumstances) and is robust in different environments. Our SR network can also be used in word recognition tasks with less than ideal images as a preprocessor.
\end{abstract}

>>>>

\begin{abstract}
\label{abstract}
We use smartphones everywhere and concerns have arisen about ``€˜shoulder surfing'',™ or the act of strangers peeking at our phone in public areas. This privacy threat have been studied heavily and various countermeasures have been designed, but mainly against attackers with the naked eye. With the development of smartphones and super resolution (SR) technology, however, we believe that this threat have been underestimated, as a malicious observer can attack from farther away with the assist of his smartphone camera and SR algorithms. We underline this concern by presenting SRPeek, an end-to-end system of shoulder surfing, containing a unique multi-image SR neural network architecture designed for this task, which in this application outperforms other known SR algorithms and fills the blank space of multi-image SR. We prove that our attack is efficient, allowing a human to read 95\% of the text off a smartphone screen at 1.5m range (in the experiment's circumstances) and is robust in different environments. Our SR network can also be used in word recognition tasks with less than ideal images as a preprocessor.
\end{abstract}
